Stable Neo-Hookean Flesh Simulation

### 2019-11-25 LaTeX-Master-Vorlage/chapter/paper.tex
working on existing energies, still not happy with it

\subsection{Existing Neo-Hookean Energies}
A commonly used energy function is defined as follows (see e.g. \cite{bonet1997nonlinear}, p.148):

\[
\Psi=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}
\]

where $\lambda$ and $\mu$ are the material constants and $J = det(F)$.

In the literature appear many more different formulations of the energy. Each one consists of a 1D length term and a 3D volume term.

\textbf{1D Length Term:} This term penalizes length changes.

@@

>>>>

\subsection{Existing Neo-Hookean Energies}

In previous literature a few energies were proposed.

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l |}
    \hline
    \textbf{Energy} & \textbf{Author(s)} \\ \hline
    $\Psi_{Neo}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ & Mooney 1940 \\ \hline
    $\Psi_{\mathrm{A}}=\frac{\mu}{2}\left(I_{C}-3\right)-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ & Odgen 1997 \\ \hline
    $\Psi_{\mathrm{B}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)^{2}$ & Bower 2009 \\ \hline
    $\Psi_{\mathrm{C}}=\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+\frac{\lambda}{2}(J-1)$ & Wang and Yang 2016 \\ \hline
    \end{tabular}
    \caption{Summary of proposed energies taken from \cite{Smith:2018:SNF:3191713.3180491}}
\label{table:1}
\end{table}

Each energy formulation can be split up into a 1D length term and a 3D volume term.

\begin{table}[!htbp]
\centering
    \begin{tabular}{ | l | l | l |}
    \hline
    \textbf{Energy} & \textbf{1D length term} & \textbf{3D volume term} \\ \hline
    $\Psi_{Neo}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \ln J+\frac{\lambda}{2}(\ln J)^{2}$ \\ \hline
    $\Psi_{\mathrm{A}}$ & $\frac{\mu}{2}\left(I_{C}-3\right)$ & $-\mu \log J+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
    $\Psi_{\mathrm{B}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)$ & $+\frac{\lambda}{2}(J-1)^{2}$ \\ \hline
    $\Psi_{\mathrm{C}}$ & $\frac{\mu}{2}\left(J^{-2 / 3} I_{C}-3\right)+$ & $\frac{\lambda}{2}(J-1)$ \\ \hline
    \end{tabular}
    \caption{Energies split up into its 1D length and 3D volume term}
\label{table:1}
\end{table}

\textbf{1D Length Term:} This term penalizes length changes. Mooney proposed the energy (\cite{mooney1940theory})
\[
\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right)
\]
which was later known as "Neo-Hookean" energy.

If we expand the energy with the singular values of the deformation gradient \textbf{F} we get the following term:
\[
\Psi_{M}=\frac{\mu}{2}\left(I_{C}-3\right) = \frac{\mu}{2}\left(\sigma_{0}^2 + \sigma_{1}^2 + \sigma_{2}^2 - 3\right)
\]

The energy as it is formulated reaches its minimum at a zero volume change, meaning $I_{C}=0$ and $\Psi_{M}=-3$. Mooney added the hard constraint that $J=1$ so that the energy is minimized at the volume preserving configuration. Note that the energy is singularity free and well defined under inversion.

@@

\todoredefined[inline]{
TODO: Bonet and Wood 2008 or 1997? Table looks ugly, improve and add resources.
}
